An exploratory analysis of the influence of resource use on the yield versus quality trade-off in Australian vineyards

### 2023-08-02 article.tex
More Andrew edits

\begin{document}
\begin{linenumbers}
\begin{frontmatter}
%% Title, authors and addresses
%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \affiliation for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \affiliation{organization={},
%%            addressline={}, 
%%            city={},
%%            postcode={}, 
%%            state={},
%%            country={}}
%% \fntext[label3]{}
\title{An exploratory analysis of the influence of resource use on the yield verse quality trade-off in Australian vineyards}
%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%%
%% \affiliation[label2]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
\affiliation[label1]{organization={QUT},
  addressline={},
  city={},
  postcode={},
  state={QLD},
  country={}}
\affiliation[label2]{organization={AWRI},
  addressline={},
  city={},
  postcode={},
  state={SA},
  country={}}
\affiliation[label3]{organization={Food Agility CRC},
  addressline={},
  city={},
  postcode={},
  state={Vic},
  country={}}
\author[label1,label2,label3]{Bryce Polley}
\date{20/06/2023}
\begin{abstract}
Using a ten year dataset that spans Australia we describe the relationships of input resources to the output yield and quality of grapes for wine production. Creating a baseline for comparing the efficiency of winegrowers with regard to the tradeoff between invested resources, yield and quality. Showing that economies of scale prevail for optimising crops for yield, with larger crops producing more grapes per area. And, showing that smaller crops utilising less resources are more closely related to quality.
\end{abstract}
%%Graphical abstract`
\begin{graphicalabstract}
  \includegraphics{graphical_abstract.jpeg}
\end{graphicalabstract}'

@@

We aim to use this broad dataset to describe the relationship of input resources to the output yield and quality of vineyards. The practical addition of this aim is a baseline for comparison - given a vineyard within Australia, one could extrapolate their comparative efficiency with regard to the tradeoff between invested resources, yield and quality. In achieving this we will also confirm the existence of a yield verse quality trade off within Australian winegrowing; one not prior confirmed explicitly across such varying regions, scales and climates. 

@@

\subsubsection{Model Comparisons: Yield Verse Value}

@@

Observing Figure \ref{fig:yield_vs_value} shows an almost discrete difference between vineyards in 'Hot' areas than other regions. Comparing Figure \ref{fig:yield_vs_value} to Figure \ref{fig:yield_vs_value_area} shows almost opposing trends. However, with area coming into play in Figure \ref{fig:yield_vs_value_area}, many data points are scaled differently; specifically the vineyards from 'Hot' regions change to be found the bottom right tail end, indicating the production of large quantity of lower value grapes. An un obvious difference between the Figures, is that a large amount of the difference can be explained by rotation (being $90^\circ$ clockwise from Figure \ref{fig:yield_vs_value} to \ref{fig:yield_vs_value_area}). This is more visible when comparing both graphs to the map of regional averages for response variables, see Figure \ref{fig:map}.
There is a notable change between regional averages when looking at yield verse value. Through the coefficients we can deduce that: this difference is also a difference between more resources used for the raw response variables; and a difference between overall resource use and the size of the vineyard when considering the response variables as a ratio to area. Noting, resource use and area harvested have a combined relationship through their interactions, and separate relationships as individual variables (see Table \ref{tab:contvar}). A notable occurrence in Figure \ref{fig:yield_vs_value_area}, is that the 'Very Dry' vineyards which produce lower yields and higher quality grapes are predominantly found in the Barossa Valley (a wine region known for its high quality Shiraz). This note is important as it shows climate is not exclusively the consideration, soil and other geographical phenomenon have considerable impacts on vineyard outcomes.

@@

There was an understandably strong relationship between size and resource use, with the overall space of a vineyard and its access to resources greatly determining the upper limit of potential yield. However, size was also inversely related to the potential quality, with higher quality being related to high resource inputs per area; rather than to the overall expenditure of resources. These effects were augmented by regional and yearly affects. Even given regional and yearly changes, there was a strong connection between smaller vineyards and higher quality. This could have been due to the easier management of smaller properties.
\subsection{Resource use and Yield verse Quality} 
 There are many on-the-ground decisions that influence both quality and yield. Comparing the $R^2$ values between Models 2 and 4 showed that the average price per tonne of grapes described a great deal of the relationship between resource use and yield when variables were considered as ratios of area (due to the discrepancy in $R^2$ between the two models, see Table \ref{tab:modelsummary}). This descrepency is likely due to different vineyard prioritisation, which can be described by the type of quality and quantity a vineyard aims to target. Decisions such as the prioritisation of quality over quantity, are governed by complex physical and social forces, for example: international market demands, disease pressures and natural disasters \citep{abadCoverCropsViticulture2021,cortezUsingDataMining2009,hallWithinseasonTemporalVariation2011,i.goodwinManagingSoilWater2009,kasimatiPredictingGrapeSugar2022,oliverReviewSoilPhysical2013,srivastavaNondestructiveSensingMethods2018}; with many of these occurrences being highlighted throughout the past decades vintage reports from Wine Australia \citep{wineaustraliaNationalVintageReport2019,wineaustraliaNationalVintageReport2021,wineaustraliaNationalVintageReport2022,winemakersfederationofaustraliaNationalVintageReport2013,winemakersfederationofaustraliaNationalVintageReport2014,winemakersfederationofaustraliaNationalVintageReport2015,winemakersfederationofaustraliaNationalVintageReport2016,winemakersfederationofaustraliaNationalVintageReport2017,winemakersfederationofaustraliaNationalVintageReport2018}. It is also important to consider that these reports show that the warm inland regions have seen a decline in profit during this period, whereas regions targetting quality did not. Size becomes an important consideration, as it dictates the potential capacity to produce greater volumes of grapes. However, given the comparison of value per area, regions with larger vineyards and larger vineyards in general, tend to underperform. When considering the 'Hot Very Dry' vineyards (see Figure \ref{fig:yield_vs_value_area}) These vineyards would be very competitive with only a minor increase to sale price, possibly outperforming other regions.

@@

The negative trend between size and average sales price could be a side effect of supply verse demand, especially when looking at the level of difference in production of some vineyards. Economies of scale likely played a role in determining yield but were only one consideration alongside resource use. Size was also less of a determining factor when considering quality. It is possible that the relationship of scope 1 emissions between yield and quality was closely tied to a vineyard's area; due to requiring more fuel to cover issues (such as fixing a broken irrigation pipe), where  a larger area has the potential for issues to be further away. This is further cemented when noting that most irrigation systems are diesel based, with water use being a significant variable in each model and scope 1 emissions not; scope one emissions' lack of significance and contribution given its F-statistics, could be indicative that other vineyard activities requiring fuel are not as determining factors for a vineyards grape quality. The relationship between yield, value and area was not simply about efficiently producing the most grapes; sales price and by association grape quality, are integral to the profitability, and this is strongly linked to resource-use and thus the longevity and sustainability of a vineyard.

@@

Some regions appeared to produce many low quality grapes at scale whilst others focussed on producing higher quality grapes in lower volumes. This behaviour can also be observed when reviewing Wine Australia's annual reports, where it is apparent that some GI regions, such as the Riverland, are known for producing large amounts of lower grade (low value per tonne) grapes \cite{wineaustraliaNationalVintageReport2022,winemakersfederationofaustraliaNationalVintageReport2017}. Comparatively other regions, such as Tasmania, only produce high quality/grade grapes but in smaller quantities. The difference in pricing per tonne between the lowest and highest graded grapes can be greater than a hundred times the difference in value per tonne.

>>>>

\begin{document}
\begin{linenumbers}
\begin{frontmatter}
%% Title, authors and addresses
%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \affiliation for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \affiliation{organization={},
%%            addressline={}, 
%%            city={},
%%            postcode={}, 
%%            state={},
%%            country={}}
%% \fntext[label3]{}
\title{An exploratory analysis of the influence of resource use on the yield versus quality trade-off in Australian vineyards}
%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%%
%% \affiliation[label2]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
\affiliation[label1]{organization={QUT},
  addressline={},
  city={},
  postcode={},
  state={QLD},
  country={}}
\affiliation[label2]{organization={AWRI},
  addressline={},
  city={},
  postcode={},
  state={SA},
  country={}}
\affiliation[label3]{organization={Food Agility CRC},
  addressline={},
  city={},
  postcode={},
  state={Vic},
  country={}}
\author[label1,label2,label3]{Bryce Polley}
\date{20/06/2023}
\begin{abstract}
Using a ten year dataset that spans Australia we describe the relationships of input resources to the output yield and quality of grapes for wine production. Creating a baseline for comparing the efficiency of winegrowers with regard to the tradeoff between invested resources, yield and quality. Showing that economies of scale prevail for optimising crops for yield, with larger crops producing more grapes per area. And, showing that smaller crops utilising less resources are more closely related to quality.
\end{abstract}
%%Graphical abstract`
\begin{graphicalabstract}
  \includegraphics{graphical_abstract.jpeg}
\end{graphicalabstract}'

@@

We aim to use this broad dataset to describe the relationship of input resources to the output yield and quality of vineyards. The practical addition of this aim is a baseline for comparison - given a vineyard within Australia, one could extrapolate their comparative efficiency with regard to the tradeoff between invested resources, yield and quality. In achieving this we will also confirm the existence of a yield versus quality trade off within Australian winegrowing; one not prior confirmed explicitly across such varying regions, scales and climates. 

@@

\subsubsection{Model comparisons: yield versus value}

@@

Observing Figure \ref{fig:yield_vs_value} shows an almost discrete difference between vineyards in 'Hot' areas than other regions. Comparing Figure \ref{fig:yield_vs_value} to Figure \ref{fig:yield_vs_value_area} shows almost opposing trends. However, with area coming into play in Figure \ref{fig:yield_vs_value_area}, many data points are scaled differently; specifically the vineyards from 'Hot' regions change to be found the bottom right tail end, indicating the production of large quantity of lower value grapes. An inconspicuous difference between the Figures, is that a large amount of the difference can be explained by rotation (being $90^\circ$ clockwise from Figure \ref{fig:yield_vs_value} to \ref{fig:yield_vs_value_area}). This is more visible when comparing both graphs to the map of regional averages for response variables, see Figure \ref{fig:map}.
There is a notable change between regional averages when looking at yield versus value. Through the coefficients we can deduce that: this difference is also a difference between more resources used for the raw response variables; and a difference between overall resource use and the size of the vineyard when considering the response variables as a ratio to area. Noting, resource use and area harvested have a combined relationship through their interactions, and separate relationships as individual variables (see Table \ref{tab:contvar}). A notable occurrence in Figure \ref{fig:yield_vs_value_area}, is that the 'Very Dry' vineyards which produce lower yields and higher quality grapes are predominantly found in the Barossa Valley (a wine region known for its high quality Shiraz). This note is important as it shows climate is not exclusively the consideration, soil and other geographical phenomenon have considerable impacts on vineyard outcomes.

@@

There was an expected strong relationship between size and resource use, with the overall space of a vineyard and its access to resources greatly determining the upper limit of potential yield. However, size was also inversely related to the potential quality, with higher quality being related to high resource inputs per area; rather than to the overall expenditure of resources. Vineyard outputs were also augmented by regional and yearly affects. Even given regional and yearly changes, there was a strong connection between smaller vineyards and higher quality. This could have been due to the easier management of smaller properties.
\subsection{Resource use and yield versus quality} 
 There are many on-the-ground decisions that influence both quality and yield. Comparing the $R^2$ values between Models 2 and 4 showed that the average price per tonne of grapes described a great deal of the relationship between resource use and yield when variables were considered as ratios of area (due to the discrepancy in $R^2$ between the two models, see Table \ref{tab:modelsummary}). This descrepency is likely due to different vineyard prioritisation, which can be described by the type of quality and quantity a vineyard aims to target. Decisions such as the prioritisation of quality over quantity, are governed by complex physical and social forces, for example: international market demands, disease pressures and natural disasters \citep{abadCoverCropsViticulture2021,cortezUsingDataMining2009,hallWithinseasonTemporalVariation2011,i.goodwinManagingSoilWater2009,kasimatiPredictingGrapeSugar2022,oliverReviewSoilPhysical2013,srivastavaNondestructiveSensingMethods2018}; with many of these occurrences being highlighted throughout the past decades vintage reports from Wine Australia \citep{wineaustraliaNationalVintageReport2019,wineaustraliaNationalVintageReport2021,wineaustraliaNationalVintageReport2022,winemakersfederationofaustraliaNationalVintageReport2013,winemakersfederationofaustraliaNationalVintageReport2014,winemakersfederationofaustraliaNationalVintageReport2015,winemakersfederationofaustraliaNationalVintageReport2016,winemakersfederationofaustraliaNationalVintageReport2017,winemakersfederationofaustraliaNationalVintageReport2018}. It is also important to consider that these reports show that the warm inland regions have seen a decline in profit during this period, whereas regions targetting quality did not. Size becomes an important consideration, as it dictates the potential capacity to produce greater volumes of grapes. However, given the comparison of value per area, regions with larger vineyards (such as warmer in land regions) and larger vineyards in general, tend to underperform. When considering the 'Hot Very Dry' vineyards (see Figure \ref{fig:yield_vs_value_area}) These vineyards would be very competitive with only a minor increase to sale price, possibly outperforming other regions.

@@

The negative trend between size and average sales price could be a side effect of supply versus demand, especially when looking at the level of difference in production of some vineyards. Economies of scale likely played a role in determining yield but were only one consideration alongside resource use. Size was also less of a determining factor when considering quality. It is possible that the relationship of scope 1 emissions between yield and quality was closely tied to a vineyard's area; due to requiring more fuel to cover issues (such as fixing a broken irrigation pipe), where  a larger area has the potential for issues to be further away. This is further cemented when noting that most irrigation systems are diesel based, with water use being a significant variable in each model and scope 1 emissions not; scope one emissions' lack of significance and contribution given its F-statistics, could be indicative that other vineyard activities requiring fuel are not as determining factors for a vineyards grape quality. The relationship between yield, value and area was not simply about efficiently producing the most grapes; sales price and by association grape quality, are integral to the profitability, and this is strongly linked to resource-use and thus the longevity and sustainability of a vineyard.

@@

Some regions appeared to produce many low quality grapes at scale whilst others focussed on producing higher quality grapes in lower volumes. This behaviour can also be observed when reviewing Wine Australia's annual reports, where it is apparent that some GI regions, such as the Riverland, are known for producing large amounts of lower grade (low value per tonne) grapes \cite{wineaustraliaNationalVintageReport2022,winemakersfederationofaustraliaNationalVintageReport2017}. Comparatively other regions, such as Tasmania, only produce high quality grapes but in smaller quantities. The difference in pricing per tonne between the lowest and highest graded grapes can be greater than a hundred times the difference in value per tonne.
